LOSA Fuel Poverty maps

### 2021-09-02 LSOA Fuel poverty.Rmd

head(df)
# select the places we want

ggplot2::ggplot(df, aes(x=`Proportion of households fuel poor (%)`, 
               y=propFP)) +
  geom_point()

>>>>

head(df)
# select the places we want here

census_age$oldpop <- Census_age_fp$'Over 65s'/Census_age_fp$'Age: All usual residents; measures: Value'
ggplot(Census_age_fp, aes(x=oldpop, y=`Proportion of households fuel poor (%)`)) +
  geom_point()
